
%----------------------------------------------------------------------------------------
%	OUTREACH SECTION
%----------------------------------------------------------------------------------------


\cventry{2012--2016}{Radio Host}{Inspiration Dissemination}{KBVR FM, OSU}{Corvallis}{Co-created, produced, and hosted a weekly radio show interviewing graduate students in STEM fields about their research and experiences in graduate school.
\newline{}\newline{}
Details:
\begin{itemize}
	\item Provided opportunity for graduate students to present their research in a unique form of outreach.
	\item Actively worked with graduate students to improve their science communication skills.
	\item Assisted undergraduate media students in gaining real world audio post-production experience.
	\item Wrote weekly blog post about the week's show at \url{http://blogs.oregonstate.edu/inspiration}
\end{itemize}
}

\cventry{2012--2016}{Active Contributor}{Bioinformatics Users Group}{OSU}{}{
	Contributed presentations and discussions relevant to use of bioinformatics tools such as workflows in the R statistical environment.
}

% \cventry{2014--Present}{Steward}{Botany and Plant Pathology}{Coalition of Graduate Employees}{}{
% 	Represented and informed Botany and Plant Pathology graduate student workers about 
% }
\cventry{2012--2014}{Treasurer}{Graduate Student Association}{Department of Botany and Plant Pathology}{OSU}{
	Balanced the budget, served on bi-annual travel awards committee, helped organize and coordinate group social functions.
}

\cventry{Summer 2005}{Summer Station Manager}{}{KTRM FM, TSU}{Kirksville, MO}{
	I was the primary authority on personnel decisions, after input from team members. I organized the weekly schedule of DJs, determined the salaries of station directors and balanced a budget.
}

\cventry{2004--2007}{Radio Announcer}{}{KTRM FM, TSU}{Kirksville, MO}{
	I ensured successful operation of the transmitter, covered extra scheduled shifts to ensure KTRM stayed on air, and selected appropriate play-lists for listeners.
}

