%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Zhian N. Kamvar} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
\moveleft.5\hoffset\centerline{245 S. 15th St.} % Your address
\moveleft.5\hoffset\centerline{Philomath, OR, 97370}
\moveleft.5\hoffset\centerline{xxxxxxxxxx@science.oregonstate.edu}
\moveleft.5\hoffset\centerline{(541) 286-0187}

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------
 
%\section{OBJECTIVE}  

%A position in the field of computers with special interests in business applications programming, information processing, and management systems. 

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{EDUCATION}

{\sl Ph.D.,} Botany and Plant Pathology \\
Oregon State University, Corvallis, OR, expected 2017 \\\newline
{\sl Bachelor of Science,} Biology \\
Truman State University, Kirksville, MO, December 2007 \\
Minor: Chemistry
 
%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{TECHNICAL \\ SKILLS} 

{\sl Computer Languages:} 
R - \textsl{proficient}, Perl - \textsl{familiar}, Python - \textsl{familiar}, \\BASH - \textsl{familiar}, C - \textsl{used in the past}\\\newline
{\sl Lab Skills:} Sterile technique, DNA extraction, PCR amplification. 
 
%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{EXPERIENCE}

{\sl Graduate Research Assistant} \hfill Mar 2012 to Present \\
Gr\"unwald Lab, OSU, Corvallis, OR

\begin{itemize} \itemsep -2pt % Reduce space between items
\item Designed and executed simulation analyses for populations of partially clonal diploids. 
\item Authored an R package for genetic analysis of populations with mixed \\(sexual/clonal) reproduction. (http://cran.r-project.org/package=poppr)
\item Isolated and maintained cultures of \textit{Phytophthora syringae}.
\end{itemize}
 
{\sl Graduate Teaching Assistant} \hfill Jan 2012 to Mar 2012 \\
Biology Department, OSU, Corvallis, OR 
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Appointed as a teaching assistant for an undergraduate intro biology course for science majors.
\item Developed introductory presentations and quizzes for labs.
\item Proctored all tests and quizzes.
\item Graded assignments and provided students with timely feedback.
\item Held office hours once a week.
\end{itemize} 

{\sl Graduate Research Assistant} \hfill Aug 2011 to Dec 2011 \\
Jaiswal Lab, OSU, Corvallis, OR
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Engaged in various research projects combining bioinformatic-based text mining of databases, wet lab, and greenhouse work.
\end{itemize} 

{\sl English Instructor} \hfill Oct 2009 to Feb 2011 \\
Herald NIE, Joong-Dong, Daegu, South Korea
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Taught basic to intermediate English to Korean students ranging from Elementary to Middle School with an emphasis on task-based learning techniques.
\item Took charge of 18 different classes per week with the main task of teaching and monitoring language acquisition of each student throughout the year via monthly evaluations based on interviews and speaking tests.
\item Wrote tests, assigned and graded homework pertinent to the level of the students. Initiated and mediated interesting topics for discussion courses.
\end{itemize}

\newpage

{\sl English Instructor} \hfill Jul 2008 to Oct 2009 \\
GnB English, Sangin-2-Dong, Daegu, South Korea 
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Taught basic to intermediate English to Korean students ranging from Elementary to Middle School in tandem with one of the nine Korean English teachers at the academy.
\item Assisted with at least 30 different classes per week and monitored the language acquisition of each student throughout the year.
\item Had to be prepared for sudden changes in curriculum and classroom size.
\end{itemize} 
 
{\sl Undergraduate Research Assistant} \hfill May 2006 to Dec 2007 \\
Biology Discipline, Truman State University 
\begin{itemize} \itemsep -2pt % Reduce space between items
\item As part of a team of undergraduate students, contributed to the annotation of over 2,000 maize genes determined by microarray hybridization analysis to be involved in maize shoot apical meristem function and leaf primordial formation.
\item Became proficient in performing and interpreting BLAST and InterProScan searches on sequences, identifying and assessing pertinent primary literature, and using a variety of databases to determine the putative function of maize genes.
\item Collaborated with other researchers on the same project.
\item Research mentors: Drs. Brent Buckner and Diane Janick-Buckner.
\end{itemize} 

{\sl Undergraduate Teaching Assistant} \hfill Sep 2006/07 to Dec 2006/07 \\
Biology Discipline, Truman State University 
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Helped prepare instructional labs for students of Dr. Diane Janick-Buckner's Cell Biology students.
\item Responded to student lab questions and referred to professor those questions outside of my expertise/knowledge base.
\end{itemize} 

{\sl Radio Announcer} \hfill May 2004 to Dec 2007 \\
KTRM 88.7FM, Kirksville, MO 
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Ensured successful initial and ongoing operation of transmitter.
\item Covered extra scheduled shifts to make sure KTRM stayed on the air.
\item Selected appropriate and entertaining playlists for listeners.
\end{itemize}

{\sl Summer Station Manager} \hfill May 2005 to Aug 2005 \\
KTRM 88.7FM, Kirksville, MO 
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Primary authority on personnel decisions, after input from team members.
\item Organized weekly schedule of DJs.
\item Determined the salaries of station directors and balanced a budget.
\end{itemize}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%---------------------------------------------------------------------------------------- 

\section{PUBLICATIONS}

Buckner B, Beck J, Browning, K, Hoxha E, Grantham L, \textbf{Kamvar Z}, Lough A, Nikolova O, and Schnable PS, Scanlon MJ, and Janick-Buckner D. 2007 Involving undergraduates in the annotation and analysis of global gene expression studies: creation of a maize shoot apical meristem expression database. \textit{Genetics} \textbf{176}: 741-747

%----------------------------------------------------------------------------------------
%	PRESENTATIONS SECTION
%---------------------------------------------------------------------------------------- 

\section{PRESENT-\\ATIONS}

{\bf Poster, \sl Fungal Genetics Conference}\hfill Mar 12-17, 2013\\
Asilomar, CA
\begin{itemize} \itemsep -2pt
\item ``Poppr: An R package for genetic analysis of populations with mixed \\(clonal/sexual) reproduction.''
\end{itemize}
\newpage

%
{\bf Talk, \sl 26th Annual Biology Graduate Student Symposium}\hfill Mar 2, 2013\\
Hatfield Marine Science Center, Newport, OR
\begin{itemize} \itemsep -2pt
\item ``Poppr: An R package for genetic analysis of populations with mixed \\(clonal/sexual) reproduction.''
\end{itemize}

{\bf Poster, \sl Oregon State University Fall CGRB Conference}\hfill Sep 21, 2012\\
Corvallis, OR
\begin{itemize} \itemsep -2pt
\item ``Poppr: An R package for population genetic analysis''
\end{itemize}

{\bf Poster, \sl Truman State University Student Research Conference}\hfill Apr 3, 2007\\
Kirksville, MO
\begin{itemize} \itemsep -2pt
\item ``Annotation and Analysis of Global Gene Expression Studies: Creation of a Maize Shoot Apical Meristem Expression Database''
\end{itemize}

{\bf Poster, \sl Maize Genetics Conference}\hfill Mar 22-25, 2007\\
St. Charles, IL
\begin{itemize} \itemsep -2pt
\item ``Annotation and Analysis of Global Gene Expression Studies: Creation of a Maize Shoot Apical Meristem Expression Database''
\end{itemize}


%----------------------------------------------------------------------------------------
%	EXTRA-CURRICULAR ACTIVITIES SECTION
%----------------------------------------------------------------------------------------

\section{EXTRA-CURRICULAR \\ ACTIVITIES} 

{\sl Treasurer}\hfill Sep 2012 to Present \\
Botany and Plant Pathology Graduate Student Association, OSU
\begin{itemize} \itemsep -2pt
\item Balanced budget.
\item Issued reimbursements and travel awards.
\item Helped organize and coordinate group social functions.
\end{itemize}


{\sl Radio Co-host} \hfill Jan 2012 to Present \\
Inspiration Dissemination, 88.7FM, KBVR Corvallis
\begin{itemize} \itemsep -2pt
\item Solicited graduate and undergraduate researchers at Oregon State University to discuss their research on the radio.
\item Interviewed students to give a compelling narrative about their research and entrance into graduate school.
\end{itemize}

{\sl Active member}\hfill Sep 2012 to Present \\
Bioinformatics Users Group, OSU

%----------------------------------------------------------------------------------------

\end{resume}
\end{document}