%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,letterpaper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{casual} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{grey} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.75]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Zhian} % Your first name
\middlename{N.}
\familyname{Kamvar} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Curriculum Vitae}
\address{245 S. 15th St.}{Philomath, OR 97370}
\mobile{(541) 286-0187}
\phone{(541) 738-4074}
\email{xxxxxxxxxx@science.oregonstate.edu}
%\homepage{staff.org.edu/~jsmith}{staff.org.edu/$\sim$jsmith} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
%\extrainfo{additional information}
%\photo[70pt][0.4pt]{pictures/picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{"A witty and playful quotation" - John Smith}

%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{2011--Present}{Ph. D. Botany and Plant Pathology}{Oregon State University}{Corvallis, OR}{}{Expected 2017}  % Arguments not required can be left empty
\cventry{2003--2007}{Bachelor of Science Biology}{Truman State University}{Kirksville, MO}{}{Minor: Chemistry}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}

\subsection{Research}

\cventry{2012--Present}{Graduate Research Assistant}{Gr\"unwald Lab}{Corvallis}{OR}{
	Utilizing population genomic tools to analyze patterns of differentiation in populations of the plant pathogen \textit{Phytophthora syringae} in Oregon Nurseries.
	\newline{}\newline{}
	Details:
	\begin{itemize}
		\item Designed simulation analyses for populations of partially clonal diploids
		\item Authored R package for genetic analysis with mixed (sexual/clonal) reproduction\\ (\url{https://github.com/grunwaldlab/poppr})
		\item Isolated, maintained, and extracted DNA from cultures of \textit{Phytophthora syringae}
		\item \textbf{Research Advisor: Dr. Niklaus J. Gr\"unwald}
	\end{itemize}
}

\cventry{Fall/Winter 2011}{Graduate Research Assistant}{Jaiswal Lab}{Corvallis}{OR}{
	Engaged in various research projects combining bioinformatic-based text minining of databases, wet lab, and greenhouse work. \textbf{Research Advisor: Dr. Pankaj Jaiswal}	
}

\cventry{2006--2007}{Undergraduate Research Assistant}{Biology Discipline}{Truman State University}{Kirksville, MO}{
	As part of a team of undergraduate students, contributed to the annotation of over 2,000 maize genes determined by microarray hibridization analysis to be involved in maize shoot apical meristem functional and leaf primordial formation.
	\newline{}\newline{}
	Details:
	\begin{itemize}
		\item Became proficient in performing and interpreting BLAST and InterProScan searches on sequences, identifying and assessing pertinent primary literature, and useing a variety of databases to determine the putative function of maise genes.
		\item Collaborated with other researchers on the same project.
		\item \textbf{Research Mentors: Drs. Brent Buckner and Diane Janick-Buckner}
	\end{itemize}
}
%------------------------------------------------

\subsection{Teaching}

\cventry{Spring 2012}{Graduate Teaching Assistant}{Biology Dept.}{OSU}{Corvallis, OR}{
	Appointed as teaching assistant for undergradutate intro biology course for science majors.
	\newline{}\newline{}
	Details:
	\begin{itemize}
		\item Developed introductory presentations for quizzes and labs
		\item Proctored all tests and quizzes
		\item Graded assignments and provided students with timely feedback
		\item Held office hours once a week
	\end{itemize}
}

\cventry{2009--2011}{English Instructor}{Herald NIE}{Joong-Dong}{Daegu, South Korea}{
	Taught basic to intermediate English to Korean students ranging from elementary to middle school with an emphasis on task-based learning techniques. 
	\newline{}\newline{}
	Details:
	\begin{itemize}
		\item Took charge of 18 different classes per week
		\item Monitored language acquisition of each student via monthly evaluations based on interviews and speaking tests
		\item Wrote tests, assigned and graded homework pertinent to the level of the students. Initiated and mediated interesting topics for discussion courses
	\end{itemize}
}

\cventry{2008--2009}{English Instructor}{GnB English}{Sangin-2-Dong}{Daegu, South Korea}{
	Taught basic to intermediate English to Korean students ranging from elementary to middle school in tandem with one of the nine Korean English teachers at the academy. 
	\newline{}\newline{}
	Details:
	\begin{itemize}
		\item Assisted with at least 30 different classes per week
		\item Monitored language acquisition of students throughout the year
		\item Gained the ability to be prepared for sudden changes in cirriculum and classroom size. 
	\end{itemize}
}

\cventry{Fall Semester, 2006/07}{Undergraduate Teaching Assistant}{Biology Discipline}{Truman State University}{Kirksville, MO}{
	Appointed as teaching assistant for undergradutate cell biology course.
	\newline{}\newline{}
	Details:
	\begin{itemize}
		\item Helped prepare instructional labs for students of Dr. Diane Janick-Buckner's Cell Biology Students
		\item Responded to student lab questions and referred to professor questions ouside of my expertise/knowledge base
	\end{itemize}
}

%------------------------------------------------
\subsection{Radio}

\cventry{Summer 2005}{Summer Station Manager}{KTRM FM}{Truman State University}{Kirksville, MO}{
	I was the primary authority on personnel decisions, after input from team members. I organized the weekly schedule of DJs, determined the salaries of station directorys and balanced a budget.
}

\cventry{2004--2007}{Radio Announcer}{KTRM FM}{Truman State University}{Kirksville, MO}{
	I ensured successful operation of the transmitter, covered extra scheduled shifts to ensure KTRM stayed on air, and selected appropriate playlists for listeners.
}
%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{Awards}

\cvitem{2014}{Most Innovative Program -- Intercollegiate Broadcasting System}

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Computer skills}

\cvitem{Basic}{\textsc{bash}, Inkscape}
\cvitem{Intermediate}{\textsc{python}, \textsc{perl}, \textsc{C}, \LaTeX, OpenOffice, Linux, OSX}
\cvitem{Advanced}{\textsc{R}}

\section{Lab Skills}
\cvitem{}{Sterile Technique, DNA extraction, GBS library prep}

%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Presentations}

\subsection{Talks}

\cventry{2013/11/21}{Ph.D. Proposal Seminar}{Department of Botany and Plant Pathology}{Oregon State University}{Corvallis, OR}{Determination of pattern and process in the evolution of the plant pathogen \textit{Phytophthora syringae}}

\cventry{2013/03/02}{Conference Presentation}{Biology Graduate Student Symposium}{Hatfield Marine Science Center}{Newport, OR}{\textit{Poppr}: An R package for genetic analysis of populations with mixed (clonal/sexual) reproduction}

\subsection{Posters}

\cventry{2013/03/12-17}{Fungal Genetics Conference}{Genetics Society of America}{Asilomar}{CA}{
	\textit{Poppr}: An R package for genetic analysis of populations with mixed (clonal/sexual) reproduction 
}

\cventry{2012/09/21}{OSU Fall CGRB Conference}{Oregon State University}{Corvallis}{OR}{
	Poppr: An R package for popualtion genetic analysis
}

\cventry{2007/04/03}{TSU Student Research Conference}{Truman State University}{Kirksville}{MO}{
	Annotation and Analysis of Global Gene Expression Studies: Creation of a Maize Shoot Apical Meristem Expression Database
}

\cventry{2007/03/22-25}{Maize Genetics Conference}{}{St. Charles}{IL}{
	Annotation and Analysis of Global Gene Expression Studies: Creation of a Maize Shoot Apical Meristem Expression Database
}
%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\section{Languages}

\cvitemwithcomment{English}{Mothertongue}{}
\cvitemwithcomment{Korean}{Intermediate}{Can manage basic conversation}

\section{Extracurricular}

\cventry{2012--Present}{Radio Co-host}{Inspiration Dissemination}{KBVR}{Corvallis}{Co-created, produced, and hosted a weekly radio show interviewing graudate students in STEM fields about their research and experiences in graudate school.
\newline{}\newline{}
Details:
\begin{itemize}
	\item Provided opportunity for graduate students a unique form of outreach.
	\item Facilitated edcuation of media students by providing audio editing opportunities post producing recorded episodes.
	\item Actively worked with graduate students to improve their science communication skills.
\end{itemize}
}

\cventry{2012--Present}{Treasurer}{Graduate Student Assosication}{Department of Botany and Plant Pathology}{Oregon State University}{
	Blanced the budget, served on bi-annual travel awards committee, helped organize and coordinate group social functions.
}

\cventry{2012--Present}{Active Contributor}{Bioinformatics Users Group}{Oregon State University}{}{
	Contributed presentations and discussions relevant to use of bioinformatics tools.
}
%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Publications}

\begin{itemize}

    \item \textbf{Kamvar ZN}, Tabima JF, Gr\"unwald NJ. (2014) \textit{Poppr}: an
	R package for genetic analysis of populations with clonal, partially clonal,
	and/or sexual reproduction. PeerJ \textbf{2}: e281
	\url{http://dx.doi.org/10.7717/peerj.281}

	\item Buckner B, Beck J, Browning, K, Hoxha E, Grantham L, \textbf{Kamvar Z}, Lough A,
	Nikolova O, and Schnable PS, Scanlon MJ, and Janick-Buckner D. (2007) Involving
	undergraduates in the annotation and analysis of global gene expression studies:
	creation of a maize shoot apical meristem expression database. \textit{Genetics}
	\textbf{176}: 741-747

\end{itemize}


%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

% \clearpage

% \recipient{HR Departmnet}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
% \date{\today} % Letter date
% \opening{Dear Sir or Madam,} % Opening greeting
% \closing{Sincerely yours,} % Closing phrase
% \enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents

% \makelettertitle % Print letter title

% \lipsum[1-3] % Dummy text

% \makeletterclosing % Print letter signature

%----------------------------------------------------------------------------------------

\end{document}