%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,letterpaper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{enumitem}
\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
\usepackage{natbib}
\usepackage{bibentry}
\usepackage[scale=0.75]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

\newcommand{\bibverse}[1]{\begin{verse} \bibentry{#1}. \end{verse} }
%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Zhian} % Your first name
\middlename{N.}
\familyname{Kamvar} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Curriculum Vitae}
\address{245 S. 15th St.}{Philomath, OR 97370}
\mobile{(541) 286-0187}
\phone{(541) 738-4074}
\email{xxxxxxxxxx@gmail.com}
%\homepage{staff.org.edu/~jsmith}{staff.org.edu/$\sim$jsmith} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
%\extrainfo{additional information}
%\photo[70pt][0.4pt]{pictures/picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{"A witty and playful quotation" - John Smith}


% Uncomment for black and white links
%\AfterPreamble{\hypersetup{colorlinks,urlcolor=black,linkcolor=black}}
%----------------------------------------------------------------------------------------
\begin{document}

% If you want a cover letter to go with it. Note that this cover letter will be included
% in the pagination. 
\recipient{Dr. Sydney E. Everhart}{
		   406 Plant Science Hall\\
		   Department of Plant Pathology\\
		   University of Nebraska-Lincoln\\
		   Lincoln, NE 68583-0722} % Letter recipient
\date{\today} % Letter date
\opening{Dear Dr. Everhart,} % Opening greeting
\closing{Sincerely yours,} % Closing phrase
\enclosure[Attached]{
	Curriculum Vitae, 
	References, 
	Oregon State University Transcripts
} % List of enclosed documents

\makelettertitle % Print letter title

I am submitting my formal application for the postdoctoral scholar position 
investigating the evolution of fungicide resistance and comparative genomics in
\textit{Sclerotinia sclerotiorum}. My research interests are broadly focused on
reproducible research and the population genetics of microbial plant pathogens.
With global warming changing the environmental corner of the disease triangle,
it's important to understand the evolutionary potential of the plant pathogen
populations to adapt to changing climate and pesticide pressure. 

As sequencing becomes more cost effective, we will eventually enter an age where
we move from regularly sequencing short genomic fragments to entire genomes. Lab
notebooks are essential tools for ensuring that laboratory science is
reproducible, and when we move towards more computational research, tools
specific for reproducing these analyses are just as important. My goal is to
ensure that the work I do open and reproducible, and that I can guide others to
take advantage of these concepts. In the end, open science ensures that we can
confidently stand on the shoulders of giants.

My qualifications for this position are both computational and biological in
discipline. I have experience in several programming languages, including R,
python, perl, and C. I am also well versed in version control with git and
github and have experience with cluster computing via the Sun Grid Engine
cluster on Oregon State University's Center for Genome Research and Computing. I
additionally have experience in software development, writing the R package
\textit{poppr} for genetic analysis of clonal populations, which has >18,000
downloads from CRAN in just over 3 years. This package includes both R code,
compiled C code, and a graphical interface using R Shiny. As my degree is from a
department of botany and plant pathology, I have training in population
genomics, mycology, and plant pathology, allowing me not only to perform the
computations, but also understand the questions asked.

I hope you will consider my application for this position and I await your
response.

% \lipsum[1-3] % Dummy text

\makeletterclosing % Print letter signature

\clearpage

\makecvtitle % Print the CV title
\section{Education}
\input{./tex/Education.tex}

\section{Employment}
\input{./tex/Research.tex}

\section{Authored Software}
\input{./tex/Software.tex}

\section{Computer skills}
\input{./tex/Skills.tex}

\section{Teaching}
\input{./tex/Teaching.tex}

\section{Spoken Languages}
\input{./tex/Languages.tex}

\section{Outreach, Service, and Extracurricular Activities}
\input{./tex/Outreach.tex}

\section{Awards}
\input{./tex/Awards.tex}

% Sections in files
\input{./tex/Pubs.tex}

\newpage 

\section{Personal References}

\textbf{Hilmar Lapp}\\
Director of Informatics\\
Center for Genomic and Computational Biology\\
Duke University\\
hlapp@duke.edu\\
919-613-4661

\bigskip

\textbf{Thibaut Jombart}\\
Lecturer\\
School of Public Health\\
Imperial College London\\
t.jombart@imperial.ac.uk\\
+44 (0)20 7594 3658

\bigskip

\textbf{Niklaus Gr\"unwald}\\
Courtesy Professor\\
Botany and Plant Pathology\\
Oregon State University\\
grunwaln@science.oregonstate.edu\\
541-738-4049


\end{document}
