%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,letterpaper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{enumitem}
\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
\usepackage{natbib}
\usepackage{bibentry}
\usepackage[scale=0.75]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

\newcommand{\bibverse}[1]{\begin{verse} \bibentry{#1}. \end{verse} }

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Zhian} % Your first name
\middlename{N.}
\familyname{Kamvar} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Curriculum Vitae}
\address{245 S. 15th St.}{Philomath, OR 97370}
\mobile{(541) 286-0187}
\phone{(541) 738-4074}
\email{xxxxxxxxxx@science.oregonstate.edu}
%\homepage{staff.org.edu/~jsmith}{staff.org.edu/$\sim$jsmith} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
%\extrainfo{additional information}
%\photo[70pt][0.4pt]{pictures/picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{"A witty and playful quotation" - John Smith}

%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{2011--Present}{Ph.D. Plant Pathology}{Oregon State University (OSU)}{Corvallis, OR}{}{Expected 2017}  % Arguments not required can be left empty
\cventry{2007}{B.S. Biology}{Truman State University (TSU)}{Kirksville, MO}{}{Minor: Chemistry}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Research}
\cventry{2012--Present}{Thesis Research}{Gr\"unwald Lab}{OSU, Corvallis}{OR}{
	My goal is to determine pattern and process in the evolution of the plant 
	pathogen \textit{Phytophthora syringae} by utilizing population genomic 
	tools to analyze genetic differentiation within and among nursery 
	populations.
	\newline{}\newline{}
	Details:
	\begin{itemize}
		\item Designed simulation analyses for populations of partially clonal diploids
		\item Authored R package for genetic analysis with mixed (sexual/clonal) reproduction\\ (\url{https://github.com/grunwaldlab/poppr})
		\item Isolated, maintained, and extracted DNA from cultures of \textit{Phytophthora syringae} for the purposes of Genotyping By Sequencing.
		\item \textbf{Research Advisor: Dr. Niklaus J. Gr\"unwald}
	\end{itemize}
}

\cventry{Aug--Dec 2011}{Rotation}{Jaiswal Lab}{OSU, Corvallis}{OR}{
	Engaged in various research projects combining bioinformatic-based text mining of databases, wet lab, and greenhouse work. \textbf{Research Advisor: Dr. Pankaj Jaiswal}	
}

\cventry{2006--2007}{Undergraduate Research Assistant}{Biology Discipline}{TSU}{Kirksville, MO}{
	As part of a team of undergraduate students, contributed to the annotation of over 2,000 maize genes determined by microarray hybridization analysis to be involved in maize shoot apical meristem functional and leaf primordial formation.
	\newline{}\newline{}
	Details:
	\begin{itemize}
		\item Became proficient in performing and interpreting BLAST and InterProScan searches on sequences, identifying and assessing pertinent primary literature, and using a variety of databases to determine the putative function of maize genes.
		\item Collaborated with other researchers on the same project.
		\item \textbf{Research Mentors: Drs. Brent Buckner and Diane Janick-Buckner}
	\end{itemize}
}
%----------------------------------------------------------------------------------------
%	TEACHING EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Teaching}

\cventry{2014}{Population Genetics in R}{Workshop}{}{}{
	Co-instructed a workshop with Niklaus Gr\"unwald and Sydney Everhart. This workshop introduces tools and concepts that allow researchers to easily perform population genetic analyses in the R statistical environment. 
	\newline{}\newline{}
	Sessions:
	\begin{itemize} 
		\item \textit{May 17, 2014} Oregon State University
		\item \textit{August 9, 2014} American Phytopathology Society (APS) 2014 National Conference
	\end{itemize}
}

\cventry{Spring 2012}{Graduate Teaching Assistant}{Biology Dept.}{OSU}{Corvallis, OR}{
	Lead laboratories of $\sim$48 students in organismal diversity, organ systems, plant and animal physiology, genetics, evolution and ecology.
	\newline{}\newline{}
	Responsibilities:
	\begin{itemize}
		\item Developed introductory presentations for quizzes and labs
		\item Proctored all tests and quizzes
		\item Graded assignments and provided students with timely feedback
		\item Held office hours once a week
	\end{itemize}
}

\cventry{2009--2011}{English Instructor}{Herald NIE}{Joong-Dong}{Daegu, South Korea}{
	Taught basic to intermediate English to Korean students ranging from elementary to middle school with an emphasis on task-based learning techniques. 
	\newline{}\newline{}
	Details:
	\begin{itemize}
		\item Took charge of 18 different classes per week
		\item Monitored language acquisition of each student via monthly evaluations based on interviews and speaking tests
		\item Wrote tests, assigned and graded homework pertinent to the level of the students. Initiated and mediated interesting topics for discussion courses
	\end{itemize}
}

\cventry{2008--2009}{English Instructor}{GnB English}{Sangin-2-Dong}{Daegu, South Korea}{
	Taught basic to intermediate English to Korean students ranging from elementary to middle school in tandem with one of the nine Korean English teachers at the academy. 
	\newline{}\newline{}
	Details:
	\begin{itemize}
		\item Assisted with at least 30 different classes per week
		\item Monitored language acquisition of students throughout the year
		\item Gained the ability to be prepared for sudden changes in cirriculum and classroom size. 
	\end{itemize}
}

\cventry{Fall 2006/07}{Undergraduate Teaching Assistant}{Biology Discipline}{TSU}{Kirksville, MO}{
	Appointed as teaching assistant for undergraduate cell biology course.
	\newline{}\newline{}
	Details:
	\begin{itemize}
		\item Helped prepare instructional labs for students of Dr. Diane Janick-Buckner's Cell Biology Students
		\item Responded to student lab questions and referred to professor questions outside of my expertise/knowledge base
	\end{itemize}
}

%----------------------------------------------------------------------------------------
%	OUTREACH SECTION
%----------------------------------------------------------------------------------------
\section{Outreach and Service}

\cventry{2012--Present}{Radio Co-host}{Inspiration Dissemination}{KBVR FM, OSU}{Corvallis}{Co-created, produced, and hosted a weekly radio show interviewing graduate students in STEM fields about their research and experiences in graduate school.
\newline{}\newline{}
Details:
\begin{itemize}
	\item Provided opportunity for graduate students a unique form of outreach.
	\item Facilitated education of media students by providing audio editing opportunities post producing recorded episodes.
	\item Actively worked with graduate students to improve their science communication skills.
\end{itemize}
}

\cventry{2012--Present}{Active Contributor}{Bioinformatics Users Group}{OSU}{}{
	Contributed presentations and discussions relevant to use of bioinformatics tools.
}

\cventry{2004--2007}{Radio Announcer}{}{KTRM FM, TSU}{Kirksville, MO}{
	I ensured successful operation of the transmitter, covered extra scheduled shifts to ensure KTRM stayed on air, and selected appropriate play-lists for listeners.
}

%----------------------------------------------------------------------------------------
%	LEADERSHIP SECTION
%----------------------------------------------------------------------------------------
\section{Leadership}

\cventry{2012--Present}{Treasurer}{Graduate Student Association}{Department of Botany and Plant Pathology}{OSU}{
	Balanced the budget, served on bi-annual travel awards committee, helped organize and coordinate group social functions.
}

\cventry{Summer 2005}{Summer Station Manager}{}{KTRM FM, TSU}{Kirksville, MO}{
	I was the primary authority on personnel decisions, after input from team members. I organized the weekly schedule of DJs, determined the salaries of station directors and balanced a budget.
}


%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{Awards}

\cvitem{2014}{Most Innovative Program -- Intercollegiate Broadcasting System}
\cvitem{2013}{Seattle Institute For Statistical Genetics Travel Award -- \$450}
\cvitem{2006}{Truman State University Summer Research Stipend -- \$3000}
\cvitem{2003}{Truman State University Presidential Leadership Scholarship -- \$2000}

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Computer skills}

\cvitem{Advanced}{\textsc{R}}
\cvitem{Intermediate}{\textsc{python}, \textsc{perl}, \textsc{C}, \LaTeX, OpenOffice, Linux, OSX}
\cvitem{Basic}{\textsc{bash}, Inkscape}

%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\section{Languages}

\cvitemwithcomment{English}{Mother tongue}{}
\cvitemwithcomment{Korean}{Intermediate}{Can manage basic conversation}



\section{Peer Reviewed Publications}

\begin{enumerate}[leftmargin = 14pt]

    \item \textbf{Kamvar ZN}, Tabima JF, Gr\"unwald NJ. (2014) \textit{Poppr}: an
	R package for genetic analysis of populations with clonal, partially clonal,
	and/or sexual reproduction. PeerJ \textbf{2}: e281
	\url{http://dx.doi.org/10.7717/peerj.281}
	
	\vspace{6pt}

	\item Buckner B, Beck J, Browning, K, Hoxha E, Grantham L, \textbf{Kamvar ZN}, Lough A,
	Nikolova O, and Schnable PS, Scanlon MJ, and Janick-Buckner D. (2007) Involving
	undergraduates in the annotation and analysis of global gene expression studies:
	creation of a maize shoot apical meristem expression database. \textit{Genetics}
	\textbf{176}: 741-747 \url{http://dx.doi.org/10.1534/genetics.106.066472}

\end{enumerate}



\section{Presentations}


\begin{enumerate}[leftmargin = 14pt]
	\item \textbf{Kamvar ZN} (2013) Ph.D. Proposal Seminar: Determination of pattern and process in the evolution of the plant pathogen \textit{Phytophthora syringae}. Department of Botany and Plant Pathology, Oregon State University, Corvallis, OR.

	\vspace{6pt}

	\item \textbf{Kamvar ZN} (2013) \textit{Poppr}: An R package for genetic analysis of populations with mixed (clonal/sexual) reproduction. Biology Graduate Student Symposium, Hatfield Marine Science Center, Newport OR.

	\vspace{6pt}

	\item \textbf{Kamvar ZN}, Tabima JF, Gr\"unwald NJ (2013) \textit{Poppr}: An R package for genetic analysis of populations with mixed (clonal/sexual) reproduction. Fungal Genetics Conference, Asilomar, CA.

	\vspace{6pt}

	\item \textbf{Kamvar ZN}, Gr\"unwald NJ (2012) \textit{Poppr}: An R package for popualtion genetic analysis. OSU Fall CGRB Conference, Oregon State University, Corvallis, OR.

	\vspace{6pt}

	\item Browning K, Fritz A, Hoxha E, and \textbf{Kamvar ZN} (2007) Annotation and analysis of global gene expression studies: creation of a maize shoot apical meristem expression database, Maize Genetics Conference, St. Charles, IL.

	\vspace{6pt}

	\item Browning K, Fritz A, Hoxha E, and \textbf{Kamvar ZN} (2007) Annotation and analysis of global gene expression studies: creation of a maize shoot apical meristem expression database, Truman Student Research Conference, Truman State University, Kirksville, MO. 
\end{enumerate}

% \cventry{2013/11/21}{Ph.D. Proposal Seminar}{Department of Botany and Plant Pathology}{Oregon State University}{Corvallis, OR}{Determination of pattern and process in the evolution of the plant pathogen \textit{Phytophthora syringae}}

% \cventry{2013/03/02}{Conference Presentation}{Biology Graduate Student Symposium}{Hatfield Marine Science Center}{Newport, OR}{\textit{Poppr}: An R package for genetic analysis of populations with mixed (clonal/sexual) reproduction}

% \cventry{2013/03/12-17}{Fungal Genetics Conference}{Genetics Society of America}{Asilomar}{CA}{
% 	\textit{Poppr}: An R package for genetic analysis of populations with mixed (clonal/sexual) reproduction 
% }

% \cventry{2012/09/21}{OSU Fall CGRB Conference}{Oregon State University}{Corvallis}{OR}{
% 	Poppr: An R package for popualtion genetic analysis
% }

% \cventry{2007/04/03}{TSU Student Research Conference}{Truman State University}{Kirksville}{MO}{
% 	Annotation and Analysis of Global Gene Expression Studies: Creation of a Maize Shoot Apical Meristem Expression Database
% }

% \cventry{2007/03/22-25}{Maize Genetics Conference}{}{St. Charles}{IL}{
% 	Annotation and Analysis of Global Gene Expression Studies: Creation of a Maize Shoot Apical Meristem Expression Database
% }


%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------




%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

% \clearpage

% \recipient{HR Departmnet}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
% \date{\today} % Letter date
% \opening{Dear Sir or Madam,} % Opening greeting
% \closing{Sincerely yours,} % Closing phrase
% \enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents

% \makelettertitle % Print letter title

% \lipsum[1-3] % Dummy text

% \makeletterclosing % Print letter signature

%----------------------------------------------------------------------------------------

\end{document}