
%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

\clearpage
\begin{flushright}
  Dr. Zhian N. Kamvar\\
  Dept. of Infectious Disease Epidemiology\\
  Imperial College London, W2 1NY, UK\\
  \today
\end{flushright}

\textbf{The Carpentries}
(c/o Community Initiatives)\\
1000 Broadway, Suite \#480\\
Oakland, CA 94607, USA

% The Carpentries is committed to “training and fostering an active, inclusive,
% diverse community of learners and instructors who promote and model the
% importance of software and data in research.” We seek an engaged and
% collaborative individual who shares this vision for a full-time position as
% the Lesson Infrastructure Technology Developer for The Carpentries. The
% Lesson Infrastructure Technology Developer has a broad responsibility for
% developing infrastructure and processes to support hosting, curation, and
% discoverability of community-developed lessons.

% As the Lesson Infrastructure Technology Developer, you will create templates,
% infrastructure, and documentation for development of new curricula and
% adaptation of existing curricula to community standards. You will reduce the
% technological barriers to creating and sharing lesson materials by developing
% systems that are accessible to community members from a wide range of
% technical experience levels. The Lesson Infrastructure Technology Developer
% will design systems to enhance discoverability of curricular resources and
% develop clear rating and review systems to help the community assess
% curriculum quality and suitability for their teaching contexts. You will
% develop technical infrastructure to support lesson evaluation, deployment,
% publication, and tracking, and will engage with diverse community members to
% test and iterate on these systems. Depending on your background, skill set
% and interests, you may also contribute to the support of our technical
% infrastructure (e.g., database and systems administration).

% This role is a good fit for someone interested in transitioning from an
% academic environment to a focus on technical work, and who is interested in
% gaining experience in the non-profit space.

% Required:

    % Familiarity with the open-science, open-source community
    % Familiarity with Git and GitHub
    % Familiarity with one or more of the following: Bash, Jekyll, R, Python
    % Familiarity with HTML5, CSS
    % Experience working with the Linux operating system
    % Experience communicating technical subjects to non-technical audiences
    % Demonstrated leadership experience in professional or volunteer settings
    % Excellent written and real-time communication skills
    % Customer-service orientation
    % Ability to work with minimal supervision
    % Excellent time management skills
    % Able to work remotely with a distributed team

% Preferred:

    % Experience with The Carpentries
    % Experience working with a volunteer community
    % Experience contributing to open-source projects
    % Project management skills
    % Experience with continuous integration (e.g. Travis CI)
    % Experience working with metadata schema (e.g. Bioschema)
    % Experience or knowledge of human-centered design and accessibility
    % Experience in a system administrator role
    % Experience with Docker
    % Experience working with web APIs (including GitHub’s)
    % Experience with React or other UI frameworks
    % Experience with RMarkdown or other authoring tools
    % Experience with Amazon Web Services or other cloud providers

\vspace{1ex}
To the recruitment team,

\vspace{1ex}


I saw the position for
\href{https://static.carpentries.org/lesson-infrastructure-technology-developer/}{Lesson
Infastructure Technology Developer} via the ROpenSci slack channel and I
realized that this position is exactly what I've been looking for. I am a
research software engineer at Imperial College London
developing R packages, automated workflows, and short-course trainings for
field epidemiologists in outbreak scenarios. 
My background in science communication, \textbf{8 years experience developing R
packages and tutorials for diverse audiences}, discipline in collaborative
software engineering practices (test driven development, GitHub flow, and
continuous integration), and eagerness to learn and apply new skillsets makes
me an ideal candidate for this position. As an academic looking to transition into
technical work in the non-profit sector, I'm excited for this opportunity to
apply my skills in open-source software developement, evidence-based teaching,
and communication to the challenge of strenghthening the Carpentries'
infastructure. 

\vspace{1ex}

    % Familiarity with the open-science, open-source community
    % Familiarity with Git and GitHub
    % Familiarity with one or more of the following: Bash, Jekyll, R, Python
    % Familiarity with HTML5, CSS

    % Experience working with the Linux operating system
    % Experience communicating technical subjects to non-technical audiences
    % Demonstrated leadership experience in professional or volunteer settings
    % Excellent written and real-time communication skills
    % Customer-service orientation

    % Ability to work with minimal supervision
    % Excellent time management skills
    % Able to work remotely with a distributed team



My skill set lies in the intersection between software development,
reproducible research, open science, and communication.  \textbf{I have been
collaboratively developing open source software on GitHub
since 2013}. My most successful software project is the R package
\textit{poppr}, which has been \textbf{featured in \textgreater500
peer-reviewed scientific publications}. I strongly believe this project was
successful because I took a `customer-service' approach.  With
human-centered design, clear documentation, tutorials, workshops, and diligent
forum moderation, this approach \textbf{significantly reduced the barrier for
population genetic analysis in R}.

\vspace{1ex}

My work in lesson and workshop management gives me much of the experience
needed to be effective for this role. \textbf{Over the past 5 years, I have
collaboratively designed 4 introductory workshops} in R programming and
reproducible research to \textbf{non-technical audiences} with backgrounds in
plant pathology, population genetics, and epidemiology. The majority of the
workshop participants reported an increase of confidence with thier ability to
use R for their work.

\vspace{1ex}

I am also \textbf{keenly aware of the infrastructural challenges of curation, hosting,
and discoverability of lessons} from my experience co-maintaining
\url{https://popgen.nescent.org}\footnote{Kamvar, Z.N., López‐Uribe, M.M.,
Coughlan, S., Grünwald, N.J., Lapp, H. and Manel, S. (2017), Developing
educational resources for population genetics in R: an open and collaborative
approach. Molecular Ecology Resources, 17: 120-128.
doi:\href{https://doi.org/10.1111/1755-0998.12558}{10.1111/1755-0998.12558}}.
This website hosts peer-reviewed vignettes of population
genetic analyses in R that are automatically built and deployed through
continuous integeration. Our main goal was to ensure that the
\textbf{technical barriers for contributors were minimized or eliminated}.

% In 2017, I worked with Dr. Sydney Everhart to create an intro to R lesson for
% plant pathologists as a template that was \textbf{designed to be easily
% modifiable} and has been shared with members in the plant pathology
% community\footnote{Initial workshop, 2017:
% \url{https://twitter.com/number_three/status/867468977651539968}}\footnote{Presented
% by Dr. Katlin Gold, 2018:
% \url{https://twitter.com/kaitlinmgold/status/1055833741418000386}}\footnote{Presented
% by Dr. Lucky Mehra, 2019:
% \url{https://twitter.com/lmehra/status/1191373603771691008}}. 

\vspace{1ex}

For the last year, \textbf{my most rewarding leadership experience} has been as one of
the technical leads on the R4EPIs\footnote{\url{https://R4EPIs.netlify.com}}
project---a collaboration between the R Epidemics Consortium (RECON) and
M\'{e}decins Sans Fronti\`{e}res (MSF)---\textbf{I have first-hand experience
in working remotely with developers and users} (many of whom were
non-technical) to design templates and eductational materials to get field
epidemiologists using R. We used an iterative human-centered design process to
ensure that the templates were built in a way that epidemiologists were 
comfortable using. 

\vspace{1ex}

The experience I have gained in the last 5 years have given me the insights and
technical knowledge needed for this position. I've been very impressed by the
work the carpentries have been doing to make software and data management in
research more friendly and accessible and I am excited for this opportunity to
become a member of the team. As requested in the instructions, the country in
which I pay taxes is the United States of America. I would like to thank the
recruitment team for considering my application. 

\vspace{2ex}

Sincerely,

\vspace{5ex}

\textbf{Zhian N. Kamvar, Ph. D.}\\
\textit{Attached: Resum\'{e}, references}



\clearpage
