
%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

\clearpage
\begin{flushright}
  Dr. Zhian N. Kamvar\\
  Dept. of Infectious Disease Epidemiology\\
  Imperial College London, W2 1NY, UK\\
  \today
\end{flushright}

\textbf{OHSU Center for Spatial Systems Biomedicine}\\
Collaborative Life Sciences Building \& Skourtes Tower\\
2730 SW Moody Ave\\
Portland, OR 97201

% Master’s Degree with major courses in relevant field (STEM) and 3 years of
% relevant experience; OR Bachelor’s Degree with major courses in field of
% research and 5 years of relevant experience
%
% Essential testing-focused skills:
% - Strong knowledge of, and success in, establishing standard testing methods,
%   tools and frameworks
% - 3-5 years of experience (depending on agree as noted above) performing
%   software quality and testing throughout product development, deployment and
%   maintenance, including 3-5 years of experience writing, running and
%   automating tests and 2 years of experience leading project-level testing
%   efforts

% Good coding skills in at least one the technologies at the core of our
% product, and familiarity with the others:  
% - SQL
% - Javascript / React
% - Python
% - Java

% Knowledge of open source, commercial, or custom developed testing tools,
% technologies, including:
% - pytest
% - pgtap
% - Selenium

% - Excellent judgment from understanding of customer and enterprise needs
% - Demonstrated strong communication, problem-solving, analytical, and
%   collaboration skills
% - Demonstrated ability to lead and guide team members; willingly takes
%   direction from others, on areas outside their expertise
% - General understanding of software development concepts, principles, and
%   theory, with demonstrated ability to follow them
% - Able to sustainably balance development with creation and maintenance of
%   testing-focused strategies and workplans; must be able to manage multiple
%   projects & tasks simultaneously
% - Quality mindset with exceptional attention to detail

% Preferred Qualifications

% Experience in architecting, designing and developing test automation frameworks from scratch
% Working knowledge with Atlassian productivity tools -- JIRA, Confluence, etc. -- or related
% Prior experience with Agile development methodologies
% Able to pick up new technologies with ease
% Experience with continuous integration work processes and systems, such as Jenkins or TeamCity
% Experience with software related to healthcare and research data management, such as:
% - Epic / Clarity
% - LabKey
% - REDCap


\vspace{1ex}
To the recruitment team,

\vspace{1ex}

I am applying for the position of Software Developer Engineer in Test. I am a
research software engineer at Imperial College London developing R packages,
automated workflows, and short-course trainings for field epidemiologists in
outbreak scenarios. My background in bionformatic data analysis, \textbf{8
years experience developing R packages} for diverse audiences, discipline in
collaborative software engineering practices (test driven development, GitHub
flow, and continuous integration), and eagerness to learn and apply new
skillsets makes me an ideal candidate for this position. Having worked as both
as a scientist and software engineer, I am excited for the opportunity to join
the OHSU Center for Spatial Systems Biology and work on developing robust and
maintainable test infastructure to support research that will improve human 
health. 

% The Software Developer Engineer in Test is responsible for designing,
% implementing, and maintaining test plans, cases, infrastructure, and work
% processes, for both data and product quality.

\vspace{1ex}

With several years of disciplined software development and analytical
research experience across two disparate fields of research, ability to rapidly
adapt to new technologies, and drive for product quality, I have all of the
desired qualifications for this position. I have been developing scientific
software in R and C since 2012 and currently maintain 5 packages on CRAN. All
of these packages are tested under continuous integration and one
(poppr\footnote{R package `poppr': \url{https://grunwaldlab.github.io/poppr}})
is featured in \textgreater500 scientific publications. \textbf{I have a solid
foundation in creating automated data-processing pipelines} and all of my
published papers have the code and data needed to reproduce the results. My
most recent first-author analytical work\footnote{\textbf{Kamvar} \textit{et al.} (2017) Population structure and
phenotypic variation of \textit{Sclerotinia sclerotiorum} from dry bean
(\textit{Phaseolus vulgaris}) in the United States. \textit{PeerJ}
\textbf{5}:e4152 doi:
\href{https://doi.org/10.7717/peerj.4152}{10.7717/peerj.4152}} is fully
reproducible in a Docker container hosted on DockerHub.

\vspace{1ex}

The idea of working as a software developer engineer in test is quite appealing to me
because this sits at the intersection of two topics I've been passionate about
for the past six years: reproducible research and robust software applications.
\textbf{I am keenly aware of the value of tests to support improvement of new and
legacy codebases.} One
concrete example\footnote{\url{https://github.com/grunwaldlab/poppr/issues/16}} is
from 2015 when a major version
update\footnote{\url{https://github.com/thibautjombart/adegenet/commit/add256cd11f37e4865e4278e6bf3ffa81bcd0f63}}
to a dependency for my software caused much of its functionality to fail, my
test suite allowed me to safely refactor to adapt to the update. For the last
year, as one of the technical leads on the R4EPIs
project\footnote{\url{https://r4epis.netlify.com}}---a collaboration between
the R Epidemics Consortium (RECON) and M\'{e}decins Sans Fronti\`{e}res
(MSF/Doctors Without Borders)---\textbf{I have first-hand experience in working closely with developers
and users} (many of whom were not proficient in R) to define verification tests
against pathologies unique to epidemiological data. We used validation tests,
continuous integration, and code review on GitHub to ensure the quality of
contributed code.

\vspace{1ex}

As my carreer focus has shifted from investigative research to scientific
software engineering, this position will be immensely beneficial to my
trajectory as a research software engineer. My background in quantitative
science, robust software development, and experience as both a developer and 
user makes me well-suited to join the OHSU Center for Spatial Systems Biology
as a software engineer in testing. Thank you for your time and consideration, I
look forward to hearing from you. 

\vspace{2ex}

Sincerely,

\vspace{5ex}

\textbf{Zhian N. Kamvar, Ph. D.}\\
\textit{Attached: Resum\'{e}, references}





% My qualifications: 

%  - Shipping R packages with C backends (poppr)
%  - Worked with data science tools such as docker containers in cloud-based infastructure (Kamvar et al. 2017)
%  - I am an autodidact and will learn new approaches/technologies to acheive my goals.
%  - Since 2013 I have worked openly and collaboratively on open source software and data analyses. 
%  - I have worked in two distributed computing frameworks (SGE and SLURM) and am knowledgable of how to properly use shared resources.

% Why you want to hire me:

%  - I have six years of experience maintaining open source software, both new and
%    legacy code in both R and C.
%  - I know how to work with data scientists to write user stories that allow me
%    to develop packages that are both user-friendly, robust, and reliable.
%  - I have experience working remotely with a diverse team using GitHub flow and 
%    continuous integration.
%  - I know how to learn new skill sets to solve unique challenges (I learned C
%    to address performance issues in R and I learned Make to create a genomic
%    data analysis pipeline).
%  - I have several years experience of collaborative working.
%  - I have strong technical writing skills.





\clearpage
