
%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

\clearpage
\begin{flushright}
  Dr. Zhian N. Kamvar\\
  Department of Infectious Disease Epidemiology\\
  Imperial College London, W2 1NY, UK\\
  \today
\end{flushright}
\recipient{Sandra Wilkins}{Director of Marketing} % Letter recipient
\date{\today} % Letter date
\opening{Dear Sandra Wilkins} % Opening greeting
\closing{Sincerely,} % Closing phrase
\enclosure[Attached]{curriculum vit\ae{}, references} % List of enclosed documents

% You will work with the RStudio tool set from wrangling raw data, optimizing
% our campaigns and sales efforts, and all the way up to designing and
% deploying executive and board dashboards. This is a critical role in helping
% RStudio learn more about our business so that we can do a better job
% delivering on our mission.

% Responsibilities:

% - You will be the first data scientist hire supporting our Sales and
%   Marketing teams
% - You will collaborate with other stakeholders to develop models of customer
%   behavior
% - You will help design, measure, and optimize customer experiences that are
%   unique and valuable
% - You will be working on the entire “stack” from raw data to experimental
%   analysis
% - You will analyze experimental results and apply what you learn to future
%   experiments
% - You will share report findings to all relevant stakeholders, including
%   non-technical stakeholders
% - You will work with Sales and Marketing leadership on setting long term
%   goals with clear deliverables and making action plans to realize them
% - You will work on a marketing attribution model, lifetime value modeling,
%   and data visualization - ability to present results clearly to technical
%   and non-technical stakeholders


% About You:

% - You are humble, kind, curious, and people smart
% - 2+ years of direct experience in a data science role, ideally working in a
%   Sales and Marketing capacity
% - Hands-on experience developing, debugging, improving models in R
% - You are highly organized, self-motivated and able to adapt to changing
%   priorities, with strong critical thinking and project management skills
% - You enjoy  working with cross-functional teams, and understand trade-offs
%   in goals and investments of resources
% - Willingness and desire to work in a fast-paced and high growth environment
% - You are able to communicate complex ideas in a straightforward, engaging
%   and informative way, that demonstrates empathy for customers struggles and
%   challenges
% - Familiarity with R (critical), Python, and RStudio products (a plus)

I am applying for the Data Scientist
position\footnote{https://hire.withgoogle.com/public/jobs/rstudiocom/view/P_AAAAAACAAJZEFtwl7GyX-U}
in the RStudio marketing and sales team. I saw this advertised by several of my
connections on twitter and I am confident that I am a good fit for this position. I am a research software engineer at Imperial College London developing R
packages, report templates, and trainings for field epidemiologists in outbreak
scenarios. My background as a research scientist, experience developing R
packages for diverse audiences, excellent communication skills, and eagerness
to learn and apply new skillsets makes me an ideal candidate for this position.
Having worked as both as a scientist and software engineer, I am excited for
the opportunity to join the marketing and sales team and help support RStudio in delivering on its mission to empower users to be productive in R. 


\vspace{1ex}

As a trained scientist who has worked in an interdisciplinary context, I have the skills needed to be successful in this role. 

I have been 
developing in R and C since 2012 and have five packages on CRAN, one of which
(\href{https://grunwaldlab.github.io/poppr}{poppr}) has \textgreater500
citations in scientific publications. Since 2013, I have been working openly and
collaboratively on GitHub using developer best practices (TDD, code review, 
GitHub flow). Moreover, I have experience working in two distributed computing
frameworks (\href{https://github.com/zkamvar/clonal-inference-simulations}{SGE}
and \href{https://github.com/zkamvar/read-processing}{SLURM}).

% \vspace{1ex}

% I've been excited about the prospect of working for RStudio because they are
% part of the driving force that made R more accessible to everyone. Moreover,
% the company culture of remote work, collaboration, and sensible time off is a
% welcome respite from moving every two years in the academic sector. 

\vspace{1ex}


My qualifications: 

 - Shipping R packages with C backends (poppr)
 - Worked with data science tools such as docker containers in cloud-based infastructure (Kamvar et al. 2017)
 - I am an autodidact and will learn new approaches/technologies to acheive my goals.
 - Since 2013 I have worked openly and collaboratively on open source software and data analyses. 
 - I have worked in two distributed computing frameworks (SGE and SLURM) and am knowledgable of how to properly use shared resources.

    % Experience shipping professional software including CRAN packages.
    % Experience in Scala or C/C++.
    % Experience in data science, machine learning or distributed computing.
    % Ability to work autonomously and independently on difficult problems.


% Desired qualifications

    % Committer in the Spark project.
    % Experience releasing and maintaining CRAN packages.
    % Experience in R, Python or Julia.
    % Experience working in open source projects.

Why you want to hire me:

 - I have six years of experience maintaining open source software, both new and
   legacy code in both R and C.
 - I know how to work with data scientists to write user stories that allow me
   to develop packages that are both user-friendly, robust, and reliable.
 - I have experience working remotely with a diverse team using GitHub flow and 
   continuous integration.
 - I know how to learn new skill sets to solve unique challenges (I learned C
   to address performance issues in R and I learned Make to create a genomic
   data analysis pipeline).
 - I have several years experience of collaborative working.
 - I have strong technical writing skills.


\vspace{1ex}

Collaboaration is an important part of my research in that I have never worked
on a single project without contributing to someone else's. In the case of
\textit{poppr}, I contributed heavily to the \textit{adegenet} package during
and after a 2015 NESCENT Population Genetics in R hackathon. In the case of
Kamvar \textit{et al.} 2017, I was able to track down and fix a
\href{https://github.com/slowkow/ggrepel/issues/72}{hidden bug} in the
\textit{ggrepel} package. Most recently, I am one of the technical leads on a
collaboration between the R Epidemics Consortium (RECON) and M\'{e}decins Sans
Fronti\`{e}res (MSF) called R4EPIs where we work on standardizing analyses and
training for field epidemiologists.  

\vspace{1ex}

As my carreer focus has shifted from investigative research to scientific
software engineering, I believe this project will be immensely beneficial to my
trajectory as a research software engineer. My background in quantitative
science, robust software development, collaborative capacity, and passion for
both equity and fairness in peer review makes me well-suited to join the team
as a software research scientist. Thank you for your time and consideration, I
look forward to hearing from you. 

\vspace{2ex}

Sincerely,

\vspace{5ex}

\textbf{Zhian N. Kamvar}\\
\textit{Attached: curriculum vit\ae{}, references}
\clearpage

%----------------------------------------------------------------------------------------


% EcoHealth Alliance seeks a creative, dedicated, and collaborative software
% research scientist to support a two-year project in launching a new software
% peer-review initiative. The software research scientist will work on the
% Sloan Foundation supported rOpenSci project, with rOpenSci staff and a
% statistical methods editorial board. They will research and develop standards
% and review guidelines for statistical software, publish findings, and develop
% R software to test packages against those standards. The software research
% scientist will work with staff and the board to collaborate broadly with the
% statistical and software communities to gather input, refine and promote the
% standards, and recruit editors and peer reviewers. The candidate must be
% self-motivated, proactive, collaborative and comfortable working openly and
% reproducibly with a broad online community.

% DESCRIPTION AND RESPONSIBILITIES

% - Research standards and protocols for evaluating statistical software
% - quality and correctness, and the extent of their adoption
% - Create new testing frameworks for R packages
% - Assist rOpenSci staff and project board members in drafting new
% - peer-review evaluation standards, guidelines, and documentation
% - Write technical and scientific papers, documentation, and blog posts
% - Assist in organizing peer-review system for scientific software and
% - managing the review board
% - Participate in and represent the rOpenSci project in person and via
% - on-line fora
% - Participate in other projects and tasks as required or assigned by
% - supervisor

% MINIMUM QUALIFICATIONS

% - A Master's degree in statistics, computer science, or a related field with
% - a focus on quantitative methodologies, or equivalent experience in
% - statistical methods evaluation and development
% - Expertise in open-source R package development, including collaborative
% - development using Git and GitHub, testing frameworks, and continuous
% - integration
% - Strong writing skills
% - Experience in collaborative team projects and consensus building
% - A passion for improving scientific reproducibility

% DESIRED QUALIFICATIONS

% - A PhD in statistics, computer science, or a related field with a focus on
% - quantitative methodologies, or equivalent experience in statistical
% - methods evaluation and development
% - Published scientific or technical articles or software documentation



