
%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

\clearpage
\begin{flushright}
  Dr. Zhian N. Kamvar\\
  17899 NW Sedgewick Ct\\
  Beaverton, OR 97006\\
  \today
\end{flushright}

\textbf{To whom it may concern}

\vspace{2ex}

I found this position on the rOpenSci slack channel via Kara Woo. After
speaking with her about the nature of the job, I am confident that I will excel
in this role. As you can see from my resum\'{e}, I have \textbf{more than 10
years of experience} collaborating with researchers to develop \textbf{robust
and well-tested R packages} in the fields of population genetics, education,
and epidemiology. Over the last 5 years, I have focused heavily on
\textbf{using R in mission-critical live deployment contexts}, which makes me
particularly fit for this role. Moreover, I am excited about this position
because it would give me the opportunity to hone my skill set and I would have
the opportunity to work with other developers in a fast-paced and challenging
environment.

\vspace{2ex}

One project I am particularly proud of is The Carpentries Workbench\footnote{Workbench user manual: \url{https://carpentries.github.io/workbench}}, 
a suite of R packages designed to build, deploy, and audit \textbf{reproducible
data science lessons} built with R Markdown in a \textbf{robust and platform indpendent} manner\footnote{Workbench developer's guide: \url{https://carpentries.github.io/workbench-dev/intro.html\#sec-remote}}.
This was a ground-up redesign of the lesson infrastructure to focus on
the needs and working practices of our diverse community of volunteers,
allowing them to focus on the content of their lesson and not the tooling.
This system, deployed in early 2023, is still in production today with no
downtime and requires minimal maintenance. This was only possible because I was
careful to ensure that it was \textbf{scalable and robust from the beginning}
and had implemented layers of integration testing.

\vspace{2ex}

In my current role as a research software engineer at UMass, I work with a
small team of developers to support collaborative modeling efforts for
infectious disease forecasting using a framework of complex data standards
and a suite of R packages for validation of model outputs. In my short tenure
here, I used my knowledge of \textbf{CI/CD to significantly improve the
deployment and testing context} for these tools to ensure quality and
reliability. I also implemented a dashboard that would display forecast
predictions and model evaluations with minimal setup, effort, and maintenance. 

\vspace{2ex}

The experience I have gained over the last decade has given me the technical
and practical experience needed to be a successful senior software engineer.
With my expertise in software development, production, and communication, I am
uniquely able to rapidly adapt to any situation and contribute to a
collaborative and friendly culture of work. I have the skills required for this
role, and am always excited about the challenge to turn complex analyses into
well-tested production code. I would like to thank the recruitment team for
consideration of my application.

\vspace{3ex}

Sincerely,

\vspace{4ex}

\textbf{Zhian N. Kamvar, Ph. D.}\\
{\footnotesize \textit{(Attached: Resum\'{e})}}

\clearpage

%----------------------------------------------------------------------------------------


